---
title: "Research paper_Early Result"
author: "Ngan Nguyen"
date: "2025-11-11"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(dplyr)
library(ggplot2)
library(readxl)
library(tidyr)
library(tidyverse)
library(purrr)
library(stringr)
library(scales)

```

# I/ Data Cleaning
```{r, message = FALSE}
total_intstudents_us <- read.csv("total_intstudents_us.csv")
```

## 1/ Total students studying in the United States from 2014 to 2023
```{r}
# Remove columns & row with only empty
total_intstudents_us_new <- total_intstudents_us %>%
  select(where(~ any(!is.na(.)))) %>%
  filter(rowSums(is.na(.)) < ncol(.))
# Rename the first cell in first column to "Academic_year"
total_intstudents_us_new[1,1] <- "Academic_year"
total_intstudents_us_new[2,1] <- "Academic_level"
colnames(total_intstudents_us_new)[1] <- "Country"
# Drop any columns that have "OPT" or "Other" or "Non-Degree"
total_intstudents_us_new <- total_intstudents_us_new[, !(total_intstudents_us_new[2, ] %in% c("Other", "OPT", "Non-Degree"))]
# Loop through the columns (2nd, 5th, etc.) and update them
for (j in seq(2, ncol(total_intstudents_us_new), by = 2)) {
  value <- total_intstudents_us_new[1, j]  # Get the value from the current column (e.g., Year_1, Year_4)
  
# Assign the value to the next two columns (spread across Year_2, Year_3, Year_5, Year_6)
  if (j + 1 <= ncol(total_intstudents_us_new)) total_intstudents_us_new[1, j + 1] <- value}


```


```{r}
# Convert the data set
# Take first two column for transpose
header_rows <- total_intstudents_us_new[1:2, ]
header_tidy <- as.data.frame(t(header_rows), stringsAsFactors = FALSE)
names(header_tidy) <- c("Academic_year", "Academic_level")
header_tidy <- header_tidy[-1, ] |> as_tibble()

# Step 2: Extract academic years and levels from the first two rows
academic_years <- as.character(total_intstudents_us_new[1, ])
academic_levels <- as.character(total_intstudents_us_new[2, ])

# Step 3: Create combined column names
col_names <- paste0(academic_years, "_", academic_levels)

# Step 4: Assign proper column names
names(total_intstudents_us_new) <- col_names

# Step 5: Remove the first two rows (since they are headers)
data_clean <- total_intstudents_us_new[-c(1, 2), ]

# Step 6: Rename the first column as "Country"
names(data_clean)[1] <- "Country"

# Step 7: Convert from wide to long format
data_long <- data_clean %>%
  pivot_longer(
    cols = -Country,
    names_to = "Year_Level",
    values_to = "total_students_each_year"
  )

# Step 8: Split combined column into Academic_year and Academic_level
data_long <- data_long %>%
  separate(Year_Level, into = c("Academic_year", "Academic_level"), sep = "_")

# Step 9: (Optional) Join with header_tidy to ensure matching year/level pairs
final_data <- data_long %>%
  inner_join(header_tidy, by = c("Academic_year", "Academic_level"))

# Step 10: Reorder columns
final_data <- final_data %>%
  select(Country, Academic_year, Academic_level, total_students_each_year)
# Step 11: make sure to add the study destination "united_states" for this data set
final_data <- final_data %>%
  mutate(study_destination = "United States")
# Filter only have asian countries
asian_countries <- c(
  "China", "India", "Kazakhstan", "Vietnam", "Afghanistan", "Bangladesh", "Bhutan", "Brunei", "Cambodia", "Indonesia", "Laos", "Malaysia", "Maldives", "Burma/Myanmar", "Nepal", "Pakistan", "Philippines", "Singapore", "Sri Lanka", "Thailand", "Timor-Leste", "South Korea", "North Korea", "Hong Kong", "Japan", "Mongolia", "Kyrgyzstan", "Tajikistan", "Turkmenistan", "Uzbekistan", "Macau"
)

# Assuming your final combined dataset is called combined_data
final_data <- final_data %>%
  filter(Country %in% asian_countries)
# Convert the column "total_students_each_year" to be value
final_data$total_students_each_year <- as.integer(final_data$total_students_each_year)

# Group by Academic_year and Country, then sum total_students_each_year
final_data_us_by_aclevel <- final_data %>%
  group_by(Academic_year, Country,study_destination) %>%
  summarise(total_students = sum(total_students_each_year, na.rm = TRUE))

# Convert to the ending year (e.g. "2001", "2002", etc.)
final_data_us_by_aclevel$Academic_year <- as.numeric(sub(".*/", "20", final_data_us_by_aclevel$Academic_year))
```



## 2/ Total students studying in Europe Country from 2014 to 2023


```{r, message = FALSE, warning=FALSE}
# Define folder
folder_path <- "~/Downloads/studydestination_europe"

# List all CSV files (use full paths so R reads from the correct folder)
files <- list.files(path = folder_path, pattern = "\\.csv$", full.names = TRUE)

# Function to clean each dataset
clean_europe_data1 <- function(file) {
  # Read the main data (skip metadata)
  europe_data1 <- read.csv(file, skip = 9)
  
  # Keep only the first 43 rows
  europe_data1 <- europe_data1[1:43, , drop = FALSE]
  
  # Remove odd-numbered columns starting from the 3rd
  cols_to_remove1 <- seq(3, ncol(europe_data1), by = 2)
  europe_data1 <- europe_data1[, -cols_to_remove1, drop = FALSE]
  
  # Read the raw file (no skip) to extract country and academic level
  raw_data1 <- read.csv(file, header = FALSE)
  
  # Extract metadata
  country_name1 <- as.character(raw_data1[7, 3])
  academic_level1 <- as.character(raw_data1[9, 3])
  
  # Safety check in case file has fewer than 11 columns
  max_col <- min(11, ncol(europe_data1))
  if (ncol(europe_data1) >= 2) {
    new_colnames1 <- as.character(unlist(europe_data1[1, 2:max_col]))
    names(europe_data1)[2:max_col] <- new_colnames1
  }
  
  # Remove that first row (used for column names) and GEO labels and total of European Union
  europe_data1 <- europe_data1[-c(1:4), , drop = FALSE]
  
  # --- Rename first column to "Country" ---
 cols_to_convert <- 2:min(11, ncol(europe_data1))
  europe_data1[, cols_to_convert] <- lapply(
    europe_data1[, cols_to_convert],
    function(x) {
      # Remove commas, trim spaces
      x_clean <- gsub(",", "", x)
      x_clean <- trimws(x_clean)
      # Convert to numeric
      x_num <- as.numeric(x_clean)
      # Replace NA with 0
      x_num[is.na(x_num)] <- 0
      return(x_num)
    }
  )
  # Add new columns
  europe_data1$country <- country_name1
  europe_data1$academic_level <- academic_level1
  europe_data1$source_file <- basename(file)

  return(europe_data1)
}
  
# Apply cleaning function to all files
all_europe_data1 <- lapply(files, clean_europe_data1)
```



```{r message = FALSE}
# Sum up by year and academic level, country
all_summarized <- lapply(all_europe_data1,function(df) {
  df %>%
    pivot_longer(
      cols = 2:11,
      names_to = "Academic_year",
      values_to = "total_students"
    ) %>%
    group_by(Academic_year, country) %>%
    summarise(total_students_each_year = sum(total_students, na.rm = TRUE)) %>%
    ungroup()
})
```

```{r}
# Put all data in one place (one dataset) together
final_data_europe_by_aclevel <- bind_rows(all_summarized)
final_data_europe_by_aclevel <- final_data_europe_by_aclevel %>%
  mutate(study_destination = "Europe")

```

```{r}
View(final_data_europe_by_aclevel)
```


```{r}
names(final_data_europe_by_aclevel)[2] <- "Country"
final_data_europe_by_aclevel$Country[final_data_europe_by_aclevel$Country == "Macao"] <- "Macau"
final_data_europe_by_aclevel$Country[final_data_europe_by_aclevel$Country == "Brunei Darussalam"] <- "Brunei"
final_data_europe_by_aclevel$Country[final_data_europe_by_aclevel$Country == "Myanmar/Burma"] <- "Burma/Myanmar"
final_data_europe_by_aclevel$Country[final_data_europe_by_aclevel$Country == "Viet Nam"] <- "Vietnam"

# Group by one more time 
final_data_europe_by_aclevel1 <- final_data_europe_by_aclevel %>%
  filter(Country %in% asian_countries) %>%
  group_by(Academic_year, Country, study_destination) %>%
   summarise(total_students= sum(total_students_each_year, na.rm = TRUE))
             
final_data_europe_by_aclevel1$Academic_year <- as.numeric(final_data_europe_by_aclevel1$Academic_year)

combined_data <- bind_rows(final_data_europe_by_aclevel1, final_data_us_by_aclevel) %>%
  filter(Academic_year >= 2014 & Academic_year <= 2023)
```

## 3/ Economic/Social indicators 

### GDP (current $USD)
```{r}
gdp <- read.csv("GDP.csv", header = FALSE)
# Remove the first 2 rows
gdp1 <- gdp[-c(1,2), , drop = FALSE]

# Use the first row as column names
colnames(gdp1) <- as.character(unlist(gdp1[1, ]))

# Remove the first row from the data
gdp1 <- gdp1[-1, ]
# Rename first column to Country
colnames(gdp1)[1] <- "Country"
# Remove the last missing column
missing_col_index <- which(colnames(gdp1) == "" | is.na(colnames(gdp1)))
missing_col_index
gdp1 <- gdp1[, -missing_col_index]
# Fix the countries naming for merging later
gdp1$Country[gdp1$Country == "Macao"] <- "Macau"
gdp1$Country[gdp1$Country == "Brunei Darussalam"] <- "Brunei"
gdp1$Country[gdp1$Country == "Myanmar/Burma"] <- "Burma/Myanmar"
gdp1$Country[gdp1$Country == "Korea, Rep."] <- "South Korea"
gdp1$Country[gdp1$Country == "Korea, Dem. People's Rep."] <- "North Korea"
gdp1$Country[gdp1$Country == "Viet Nam"] <- "Vietnam"
gdp1$Country[gdp1$Country == "Lao PDR"] <- "Laos"
gdp1$Country[gdp1$Country == "Myanmar"] <- "Burma/Myanmar"
gdp1$Country[gdp1$Country == "Hong Kong SAR, China"] <- "Hong Kong"
gdp1$Country[gdp1$Country == "Kyrgyz Republic"] <- "Kyrgyzstan"
gdp1$Country[gdp1$Country == "Macao SAR, China"] <- "Macau"

# Filter gdp1 based on those countries
gdp1_filtered <- gdp1 %>% filter(Country %in% asian_countries)

```



```{r}
# Change the year naming (ex: 2022/23 to 2023) and convert to numerical
numeric_data <- gdp1_filtered %>%
  select(Country, matches("^[0-9]{4}"))   # selects all 4-digit year columns

# Step 2: Pivot all year columns into long format
long_data <- numeric_data %>%
  pivot_longer(
    cols = -Country,          # pivot all except Country
    names_to = "Academic_year",        # the column names become the 'year' variable
    values_to = "gdp"         # the values become 'gdp'
  )

# Step 3: (Optional) Sum GDP by country and year
yearly_sum_df <- long_data %>%
  group_by(Country, Academic_year) %>%
  summarise(gdp = sum(gdp, na.rm = TRUE), .groups = "drop")
yearly_sum_df$Academic_year <- as.numeric(yearly_sum_df$Academic_year)
```

### net_immigration
```{r}
net_immigration <- read.csv("net_immigration.csv", header = FALSE)
# Remove the first 4 rows
net_immigration1 <- net_immigration[-c(1:4), , drop = FALSE]

# Use the first row as column names
colnames(net_immigration1) <- as.character(unlist(net_immigration1[1, ]))

# Remove the first row from the data
net_immigration1 <- net_immigration1[-1, ]
# Rename first column to Country
colnames(net_immigration1)[1] <- "Country"
# Filter gdp1 based on those countries

net_immigration1$Country[net_immigration1$Country == "Macao"] <- "Macau"
net_immigration1$Country[net_immigration1$Country == "Brunei Darussalam"] <- "Brunei"
net_immigration1$Country[net_immigration1$Country == "Myanmar/Burma"] <- "Burma/Myanmar"
net_immigration1$Country[net_immigration1$Country == "Korea, Rep."] <- "South Korea"
net_immigration1$Country[net_immigration1$Country == "Korea, Dem. People's Rep."] <- "North Korea"
net_immigration1$Country[net_immigration1$Country == "Viet Nam"] <- "Vietnam"
net_immigration1$Country[net_immigration1$Country == "Lao PDR"] <- "Laos"
net_immigration1$Country[net_immigration1$Country == "Myanmar"] <- "Burma/Myanmar"
net_immigration1$Country[net_immigration1$Country == "Hong Kong SAR, China"] <- "Hong Kong"
net_immigration1$Country[net_immigration1$Country == "Kyrgyz Republic"] <- "Kyrgyzstan"
net_immigration1$Country[net_immigration1$Country == "Macao SAR, China"] <- "Macau"

net_immigration1_filtered <- net_immigration1 %>% filter(Country %in% asian_countries)
# 
numeric_data1<- net_immigration1_filtered %>%
  select(Country, matches("^[0-9]{4}"))   # selects all 4-digit year columns

long_data1 <- pivot_longer(numeric_data1, 
                          cols = -Country,
                          names_to = "Academic_year",     # Convert column names (the years) into a "year" column
                          values_to = "value")   # Corresponding values go into a "value" column

# Step 3: (Optional) Sum the values for each year
yearly_sum_net_df <- long_data1 %>%
  group_by(Country, Academic_year) %>%
  summarise(total_value = sum(value, na.rm = TRUE))

yearly_sum_net_df <- yearly_sum_net_df %>%
  rename(net_immigration = total_value)  %>% filter(Country %in% asian_countries)


yearly_sum_net_df$Academic_year <- as.numeric(yearly_sum_net_df$Academic_year)

# Step 4: Print the resulting data
print(yearly_sum_net_df)
```



### unemployment rate

```{r}
unemployment_rate <- read.csv("unemployment_rate.csv", header = FALSE)

```

```{r}
# Remove the first 2 rows
unemployment_rate1 <- unemployment_rate[-c(1,2), , drop = FALSE]

# Use the first row as column names
colnames(unemployment_rate1) <- as.character(unlist(unemployment_rate1[1, ]))

# Remove the first row from the data
unemployment_rate1 <- unemployment_rate1[-1, ]

```

```{r}
colnames(unemployment_rate1)[1] <- "Country"
# Re,move the last missing column
missing_col_index2 <- which(colnames(unemployment_rate1) == "" | is.na(colnames(unemployment_rate1)))
missing_col_index2
unemployment_rate1 <- unemployment_rate1[, -missing_col_index2]


unemployment_rate1$Country[unemployment_rate1$Country == "Macao"] <- "Macau"
unemployment_rate1$Country[unemployment_rate1$Country == "Brunei Darussalam"] <- "Brunei"
unemployment_rate1$Country[unemployment_rate1$Country == "Myanmar/Burma"] <- "Burma/Myanmar"
unemployment_rate1$Country[unemployment_rate1$Country == "Korea, Rep."] <- "South Korea"
unemployment_rate1$Country[unemployment_rate1$Country == "Korea, Dem. People's Rep."] <- "North Korea"
unemployment_rate1$Country[unemployment_rate1$Country == "Viet Nam"] <- "Vietnam"
unemployment_rate1$Country[unemployment_rate1$Country == "Lao PDR"] <- "Laos"
unemployment_rate1$Country[unemployment_rate1$Country == "Myanmar"] <- "Burma/Myanmar"
unemployment_rate1$Country[unemployment_rate1$Country == "Hong Kong SAR, China"] <- "Hong Kong"
unemployment_rate1$Country[unemployment_rate1$Country == "Kyrgyz Republic"] <- "Kyrgyzstan"
unemployment_rate1$Country[unemployment_rate1$Country == "Macao SAR, China"] <- "Macau"




# Filter gdp1 based on those countries
unemployment_rate1_filtered <- unemployment_rate1 %>% filter(Country %in% asian_countries)
# View the filtered data
head(unemployment_rate1_filtered)
```

```{r}
# Change the year naming (ex: 2022/23 to 2023) and convert to numerical
numeric_data2<- unemployment_rate1_filtered %>%
  select(Country, matches("^[0-9]{4}"))   # selects all 4-digit year columns

long_data2 <- pivot_longer(numeric_data2, 
                          cols = -Country,
                          names_to = "Academic_year",     # Convert column names (the years) into a "year" column
                          values_to = "value")   # Corresponding values go into a "value" column

# Step 3: (Optional) Sum the values for each year
yearly_sum_unemployment_df <- long_data2 %>%
  group_by(Country, Academic_year) %>%
  summarise(total_value = sum(value, na.rm = TRUE))

yearly_sum_unemployment_df <- yearly_sum_unemployment_df %>%
  rename(unemployment_rate = total_value)  %>% filter(Country %in% asian_countries)

yearly_sum_unemployment_df$Academic_year <- as.numeric(yearly_sum_unemployment_df$Academic_year)

```


```{r}
# Perform a left join to add gdp, net_immigration and total_uemployment_rate to combined_data based on 'year' and 'Academic_year'
combined_data_with_total_value <- combined_data %>%
  left_join(yearly_sum_df, by = c("Academic_year" = "Academic_year", "Country" = "Country")) %>%
  left_join(yearly_sum_net_df, by = c("Academic_year" = "Academic_year", "Country" = "Country")) %>%
  left_join(yearly_sum_unemployment_df, by = c("Academic_year" = "Academic_year", "Country" = "Country"))
```



# II/ Early Results

## Multiple linear regressions of Percentage change in total Asian students between two Study destination from 2014 to 2023
```{r}
#  Aggregate total students by year and study destination ( calculate percentage change over years for each countries)
aggregated_data <- combined_data_with_total_value %>%
    filter(!Country %in% c( "China","India", "Vietnam")) %>%
  group_by(Academic_year, study_destination) %>%
  summarise(total_students = sum(total_students, na.rm = TRUE)) %>%
  arrange(study_destination, Academic_year) %>%
  group_by(study_destination) %>%
  # Compute year-over-year % change
  mutate(pct_change_students = (total_students - lag(total_students)) / lag(total_students) * 100) %>%
  ungroup()

# Plot % change over time
ggplot(aggregated_data, aes(x = Academic_year, y = pct_change_students, 
                            color = study_destination, group = study_destination)) +
  geom_line(size = 1) +
  geom_point(size = 2) +
   geom_vline(xintercept = 2020, linetype = "dashed", color = "black", size = 0.8) +
  annotate("text", x = 2020.2, y = max(aggregated_data$pct_change_students, na.rm = TRUE),
           label = "COVID-19 Travel restrictions ", hjust = 0, vjust = 1, size = 2.7, color = "black") +
  labs(
    title = "Figure 1: Percentage change in Total Students comming from 28 Asian countries",
    subtitle = "(China, India, and Vietnam excluded)",
    x = "Year",
    y = "Change in Total Students (%)",
    color = "Study Destination"
  ) +
  theme_minimal() +
  theme(plot.title = element_text(size = 12,  hjust = 0.5),
        plot.subtitle = element_text(size = 11, hjust = 0.5),
        axis.text.x = element_text(angle = 45, hjust = 1))
```

## Linear regression of Percentage change in total Asian students between two Study destination from 2014 to 2023 with economic and social indicators

```{r}
# Include the percentage change over year in combined_data_with_total_value
combined_data_with_total_value1 <- combined_data_with_total_value %>%
  arrange(study_destination, Academic_year) %>%  
  group_by(study_destination) %>%       
  mutate(pct_change_students = (total_students - lag(total_students)) / lag(total_students) * 100) %>%
  ungroup()


# Create binary columns for Country
country_binary <- model.matrix(~ Country - 1, data = combined_data_with_total_value1)
# Create binary columns for Study destination
destination_binary <- model.matrix(~ study_destination - 1, data = combined_data_with_total_value1)

# Combine with original data (excluding original categorical columns)
selected_data_binary <- cbind(
  combined_data_with_total_value1 %>% select(-Country, -study_destination, -total_students),
  country_binary,
  destination_binary
)
# Regression model of all data set
lm_preliminary_result <- lm(pct_change_students ~., selected_data_binary)
summary(lm_preliminary_result)
```


### Check the normality of the regression model
```{r}
# Residual plot
plot(lm_preliminary_result, which = 1)
```
















